Analysis of the data of lateral flow assay
--------------------------------------------------------------

Date: `r Sys.time()`
-----------------------------------------

Initial Data of first file:
-----------------------------------------
````{r, echo=FALSE}
x <- file1()
knitr::kable(x, format = "markdown")

````

Initial Data of second file:
-----------------------------------------
````{r, echo=FALSE}
x <- file2()
knitr::kable(x, format = "markdown")

````

Combined replicates:
-----------------------------------------
````{r, echo=FALSE}
x <- crep()
knitr::kable(x, format = "markdown")

````

Normalized Intensity Plot of Green QD (Normalized Intensity vs Concentration):
----------------------------------------------------------------
````{r, echo=FALSE}
x.crep <- crep()
      ni.g <- x.crep[,"Green_NI"]
      sd.g <- x.crep[,"NI.sd.green"]
      conc <- x.crep[,"Conc_CRP_Green"]
      ni.new <- as.data.frame(cbind(conc,ni.g,sd.g))
      names(ni.new) <- c("x","y","sd")
      plot1 <- ggplot(data =ni.new, aes(x,y))+ ggtitle("Intensity vs Concentration")+

        geom_point(colour = "black", na.rm = TRUE)+

        geom_smooth(method = "lm", formula = y~x, se = FALSE, colour = "black")+

        geom_errorbar(aes(ymin= y-sd, ymax=y+sd), width=.2,

                      position=position_dodge(0.05))+

        xlab("Concentration (nM)") +

        ylab("Normalized Intensity (tl/cl) [arbitrary unit]")+

        stat_poly_eq(formula = y~x, aes(label = paste(..eq.label.., ..rr.label..,

                                                      sep = "~~~")),

                     parse = TRUE)


      plot1
      
````

Normalized Intensity Plot of Green QD (0 - 15 nM) (Normalized Intensity vs Concentration):
----------------------------------------------------------------
````{r, echo=FALSE}
x.crep <- crep()
      ni.g1 <- as.data.frame(x.crep[,"Green_NI"])
      ni.g <- ni.g1[1:(nrow(ni.g1)-1),]
      sd.g1 <- as.data.frame(x.crep[,"NI.sd.green"])
      sd.g <- sd.g1[1:(nrow(sd.g1)-1),]
      conc1 <- as.data.frame(x.crep[,"Conc_CRP_Green"])
      conc <- conc1[1:(nrow(ni.g1)-1),]
      ni.new <- as.data.frame(cbind(conc,ni.g,sd.g))
      names(ni.new) <- c("x","y","sd")
      plot1 <- ggplot(data =ni.new, aes(x,y))+ ggtitle("Intensity vs Concentration")+

        geom_point(colour = "black", na.rm = TRUE)+

        geom_smooth(method = "lm", formula = y~x, se = FALSE, colour = "black")+

        geom_errorbar(aes(ymin= y-sd, ymax=y+sd), width=.2,

                      position=position_dodge(0.05))+

        xlab("Concentration (nM)") +

        ylab("Normalized Intensity (tl/cl) [arbitrary unit]")+

        stat_poly_eq(formula = y~x, aes(label = paste(..eq.label.., ..rr.label..,

                                                      sep = "~~~")),

                     parse = TRUE)


      plot1
      
````

Normalized Intensity Plot of Green QD (0 - 10 nM) (Normalized Intensity vs Concentration):
----------------------------------------------------------------
````{r, echo=FALSE}
x.crep <- crep()
      ni.g1 <- as.data.frame(x.crep[,"Green_NI"])
      ni.g <- ni.g1[1:(nrow(ni.g1)-2),]
      sd.g1 <- as.data.frame(x.crep[,"NI.sd.green"])
      sd.g <- sd.g1[1:(nrow(sd.g1)-2),]
      conc1 <- as.data.frame(x.crep[,"Conc_CRP_Green"])
      conc <- conc1[1:(nrow(ni.g1)-2),]
      ni.new <- as.data.frame(cbind(conc,ni.g,sd.g))
      names(ni.new) <- c("x","y","sd")
      plot1 <- ggplot(data =ni.new, aes(x,y))+ ggtitle("Intensity vs Concentration")+

        geom_point(colour = "black", na.rm = TRUE)+

        geom_smooth(method = "lm", formula = y~x, se = FALSE, colour = "black")+

        geom_errorbar(aes(ymin= y-sd, ymax=y+sd), width=.2,

                      position=position_dodge(0.05))+

        xlab("Concentration (nM)") +

        ylab("Normalized Intensity (tl/cl) [arbitrary unit]")+

        stat_poly_eq(formula = y~x, aes(label = paste(..eq.label.., ..rr.label..,

                                                      sep = "~~~")),

                     parse = TRUE)


      plot1
      
````

Normalized Intensity Plot of Red QD (Normalized Intensity vs Concentration):
----------------------------------------------------------------

````{r, echo=FALSE}

x.crep <- crep()
      ni.r <- x.crep[,"Red_NI"]
      sd.r <- x.crep[,"NI.sd.red"]
      conc <- x.crep[,"Conc2_IL6_Red"]
      ni.new <- as.data.frame(cbind(conc,ni.r,sd.r))
      names(ni.new) <- c("x","y","sd")
      plot1 <- ggplot(data =ni.new, aes(x,y))+ ggtitle("Intensity vs Concentration")+

        geom_point(colour = "black", na.rm = TRUE)+

        geom_smooth(method = "lm", formula = y~x, se = FALSE, colour = "black")+

        geom_errorbar(aes(ymin= y-sd, ymax=y+sd), width=.2,

                      position=position_dodge(0.05))+

        xlab("Concentration (nM)") +

        ylab("Normalized Intensity (tl/cl) [arbitrary unit]")+

        stat_poly_eq(formula = y~x, aes(label = paste(..eq.label.., ..rr.label..,

                                                      sep = "~~~")),

                     parse = TRUE)


      plot1

````

Normalized Intensity Plot of Red QD (0 - 15 nM) (Normalized Intensity vs Concentration):
----------------------------------------------------------------
````{r, echo=FALSE}

x.crep <- crep()
      ni.r1 <- as.data.frame(x.crep[,"Red_NI"])
      ni.r <- ni.r1[2:nrow(ni.r1),]
      sd.r1 <- as.data.frame(x.crep[,"NI.sd.red"])
      sd.r <- sd.r1[2:nrow(sd.r1),]
      conc1 <- as.data.frame(x.crep[,"Conc2_IL6_Red"])
      conc <- conc1[2:nrow(conc1),]
      ni.new <- as.data.frame(cbind(conc,ni.r,sd.r))
      names(ni.new) <- c("x","y","sd")
      plot1 <- ggplot(data =ni.new, aes(x,y))+ ggtitle("Intensity vs Concentration")+

        geom_point(colour = "black", na.rm = TRUE)+

        geom_smooth(method = "lm", formula = y~x, se = FALSE, colour = "black")+

        geom_errorbar(aes(ymin= y-sd, ymax=y+sd), width=.2,

                      position=position_dodge(0.05))+

        xlab("Concentration (nM)") +

        ylab("Normalized Intensity (tl/cl) [arbitrary unit]")+

        stat_poly_eq(formula = y~x, aes(label = paste(..eq.label.., ..rr.label..,

                                                      sep = "~~~")),

                     parse = TRUE)


      plot1

````

Normalized Intensity Plot of Red QD (0 - 10 nM) (Normalized Intensity vs Concentration):
----------------------------------------------------------------
````{r, echo=FALSE}

x.crep <- crep()
      ni.r1 <- as.data.frame(x.crep[,"Red_NI"])
      ni.r <- ni.r1[3:nrow(ni.r1),]
      sd.r1 <- as.data.frame(x.crep[,"NI.sd.red"])
      sd.r <- sd.r1[3:nrow(sd.r1),]
      conc1 <- as.data.frame(x.crep[,"Conc2_IL6_Red"])
      conc <- conc1[3:nrow(conc1),]
      ni.new <- as.data.frame(cbind(conc,ni.r,sd.r))
      names(ni.new) <- c("x","y","sd")
      plot1 <- ggplot(data =ni.new, aes(x,y))+ ggtitle("Intensity vs Concentration")+

        geom_point(colour = "black", na.rm = TRUE)+

        geom_smooth(method = "lm", formula = y~x, se = FALSE, colour = "black")+

        geom_errorbar(aes(ymin= y-sd, ymax=y+sd), width=.2,

                      position=position_dodge(0.05))+

        xlab("Concentration (nM)") +

        ylab("Normalized Intensity (tl/cl) [arbitrary unit]")+

        stat_poly_eq(formula = y~x, aes(label = paste(..eq.label.., ..rr.label..,

                                                      sep = "~~~")),

                     parse = TRUE)


      plot1

````

95% Confidence Interval:
-------------------------------------------------------------
````{r, echo=FALSE, results='asis'}
x <- conf_new()
knitr::kable(x, format = "markdown")

````

95% Confidence Interval (0 - 15 nM):
-------------------------------------------------------------
````{r, echo=FALSE, results='asis'}
x <- conf_new_15()
knitr::kable(x, format = "markdown")

````

95% Confidence Interval (0 - 10 nM):
-------------------------------------------------------------
````{r, echo=FALSE, results='asis'}
x <- conf_new_10()
knitr::kable(x, format = "markdown")

````

Correlation:
--------------------------------------------------------------
````{r, echo=FALSE, results='asis'}
x <- cor_new()
knitr::kable(x, format = "markdown")

````

Correlation (0 - 15 nM):
--------------------------------------------------------------
````{r, echo=FALSE, results='asis'}
x <- cor_new_15()
knitr::kable(x, format = "markdown")

````

Correlation (0 - 10 nM):
--------------------------------------------------------------
````{r, echo=FALSE, results='asis'}
x <- cor_new_10()
knitr::kable(x, format = "markdown")

````

LOD_First Method:
-----------------------------------------------------------------
````{r, echo=FALSE, results='asis'}

x <- lod_new()
knitr::kable(x, format = "markdown")

````

LOD_Second Method:
-----------------------------------------------------------------
````{r, echo=FALSE, results='asis'}

x <- lod_new2()
knitr::kable(x, format = "markdown")

````

Calculated Concentration:
-----------------------------------------------------------------
````{r, echo=FALSE, results='asis'}

x <- concentration()

knitr::kable(x, format = "markdown")

````

Settings used during implementation:
--------------------------------------------
````{r, echo=FALSE, results='asis'}

cat("Select the type of file: ", input$filetype, "\n\n")

cat("Select the type of separation for file1: ", input$decp1, "\n\n")

cat("Select the type of separation for file2: ", input$decp2, "\n\n")

cat("Intensity value: ", input$yin, "\n\n")

cat("Slope value: ", input$mslp, "\n\n")

cat("Intercept value: ", input$cint, "\n\n")

````

Session Information:
--------------------------------------------
````{r, echo=FALSE, results='asis'}

sessionInfo("Qplex")

````
